Enhancing Student Engagement via Reduction of Frustration with Programming Assignments using Machine Learning

### 2017-02-14 paper.tex
New styles

\documentclass[conference]{IEEEtran}

@@

% paper title
% Titles are generally capitalized except for words such as a, an, and, as,
% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
% not capitalized unless they are the first or last word of the title.
% Linebreaks \\ can be used within to get better formatting as desired.
% Do not put math or special symbols in the title.
\title{ 
Recognition of Student Engagement and Frustration with Programming Assignments
using Keystroke and Mouse Dynamics}

% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
\author{\IEEEauthorblockN{Kevin Bacon}
\IEEEauthorblockA{School of Electrical and\\Computer Engineering\\
Georgia Institute of Technology\\
Atlanta, Georgia 30332--0250\\
Email: http://www.kev.org/contact.html}
\and
\IEEEauthorblockN{Homer Simpson}
\IEEEauthorblockA{Twentieth Century Fox\\
Springfield, USA\\
Email: homer@thesimpsons.com}
\and
\IEEEauthorblockN{James Kirk\\ and Montgomery Scott}
\IEEEauthorblockA{Starfleet Academy\\
San Francisco, California 96678--2391\\
Telephone: (800) 555--1212\\
Fax: (888) 555--1212}}

% use for special paper notices
%\IEEEspecialpapernotice{(Invited Paper)}

% make the title area

\maketitle
\begin{abstract}

@@

\bibliographystyle{IEEEtran} 
% argument is your BibTeX string definitions and bibliography database(s) 
\bibliography{programming} 
\end{document}

>>>>

\documentclass[a4paper]{llncs}
\usepackage{subcaption} % an alternative package for sub figures
\usepackage{llncsdoc}

@@

% paper title
% Titles are generally capitalized except for words such as a, an, and, as,
% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
% not capitalized unless they are the first or last word of the title.
% Linebreaks \\ can be used within to get better formatting as desired.
% Do not put math or special symbols in the title.
\title{Enhancing Student Engagement via Reduction of Frustration with Programming Assignments using Machine Learning}

\author{Mario Garcia Valdez\inst{1}, Amaury Hernandez Aguila\inst{1}, Juan-J. Merelo\inst{2} and Alejandra Mancilla Soto\inst{1}}
\institute{ Dept. of Graduate Studies, Instituto Tecnologico de Tijuana (Mexico)\\
    \email{\tt mario@tectijuana.edu.mx}
\and
Geneura Team and CITIC, University of Granada (Spain)\\
    \email{\tt jmerelo@ugr.es}
}

% make the title area 
\maketitle

\begin{abstract}

@@

\bibliographystyle{splncs03} 
% argument is your BibTeX string definitions and bibliography database(s) 
\bibliography{programming} 
\end{document}
